---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## README Document for Assignment B2

<!-- badges: start -->
<!-- badges: end -->

The package created for this assignment provides a function called
`count_all_missing_by_group()`. This allows you to count missing
values for all columns by group. It creates a new data frame with one
row per level of group. The first column of the output data frame
contains the levels of group while the rest of the columns contain the
number of missing values for all columns in the data except those in
group.

## Installation

The `HitashaCountMissingValues` package requires the `devtools`
package be installed, as well as any dependencies the package may
have. You can do so by using install.packages("devtools").

You can install `HitashaCountMissingValues` from github by running the following code:

```{r}
devtools::install_github("stat545ubc-2023/HitashaCountMissingValues", ref= "0.1.0")
```

## Usage

This example computes the number of missing values in the `airquality`
dataset grouped by the `month` column. 

```{r} 
library(HitashaCountMissingValues)
count_all_missing_by_group(airquality, Month)
```

This example has the same output as the last example, but shows off an
alternative way of invoking the `count_all_missing_by_group()`: piping
the dataset into the function. 

```{r} 
airquality |> count_all_missing_by_group(Month) 
```

The optional `.groups` argument allows us to keep the output grouped
by the grouping column. See example below; notice how the output is a 
grouped tibble, rather than the ungrouped tibble output of the earlier
examples. 

```{r} 
count_all_missing_by_group(airquality, Month, .groups = "keep")
```

